### 2022-05-02 paper/ase22/background.tex
background

\sw{We should motivate the testing of linguistic capabilities. Give
  background of the work that has been done in CheckList: what
  capabilities they support and their limitations. Maybe find a
  motivating example?}

>>>>

%% \sw{We should motivate the testing of linguistic capabilities. Give
%%   background of the work that has been done in CheckList: what
%%   capabilities they support and their limitations. Maybe find a
%%   motivating example?}

\begin{figure}[t]
 \centering
 \lstinputlisting[language=python-pretty]{code/checklist_template.py}
 \vspace{-10pt}
 \caption{\CklstTemplateFigCaption}
 \vspace{-10pt}
\end{figure}

In this section, we provide a brief background on \Cklst testcase
generation via an example. Quality of software is verified by ensuring
the proper working of all functionalities without knowing the internal
workings of the software. Knowing performances of model on the
multiple functionalities provides users with better understanding and
debugging the software. The same principle applies to the NLP model.
traditional NLP model evaluation relying on a test set is lack of
specification of model functionality. However, In NLP domain, there
are many phenomena on linguistic input such as negation,
questionization. Given a NLP task, the phenomena determine
task-relevant output. Traditional evaluation method neglects them,
thus, it becomes less efficient to detect and analyze which aspect the
model yields unexpected outcome. To tackle this limitation, \Cklst
introduces task-dependent \lcs for monitoring model performance on
each \lc. It assumes that the linguistic phenomena can be represented
into the model behaviors as they provide what input and output are
desired and how the model works with them. For each \lc, \Cklst makes
testcase templates and generate sentences by filling-in the value for
each placeholder. We show an example of the templates in
Figure~\ref{code:TempEx}. The templates in the figure is used for
evaluating a \sa model on \SareqExThree. For the templates defined
from line~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}
have placeholders such as ${it}$, ${air_noun}$, ${pos_adj}$. Values
for the placeholders are defined at
line~\ref{code:tempex:itbe},~\ref{code:tempex:airnoun:1}
and~\ref{code:tempex:posadj:1}. Ater all, all combinations of the
values of placeholders in a template are filled-in the template, and
the senteneces are generated such as ``The flight is good'', ``That
airline was happy'' and so on. Finally, these are used for evaluation
of \lc. Despite its simplicity of testcase generation, it still has
limitations: it first relies on manual work for defining template
structure and its values. Therefore, the manual work for testcase
generation keeps the process costly. Extended from it, Second, such
manual work produces the imitative forms between test cases, and it is
likely to introduce bias on the testcases. We will show that these
observations contribute to the performance of our models.

### 2022-05-02 paper/ase22/experiment.tex
background

\paragraph{RQ1.} As described in Section \ref{sec:approach},
\tool generates test cases in two steps: specification-based seed
generation and syntax-based sentence expansion. These automated steps
may generate seed/expanded sentences marked with incorrect sentiment
labels or categorized into wrong linguistic capabilities. For example,
the search rule and template defined in a linguistic capability may
not always generate seed sentences in that capability or with the
correct label.  To answer {\bf RQ1}, we perform a manual study to
measure the correctness of the sentiment labels and linguistic
capabilities associated with the seed/expanded sentences, produced by
\tool

\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated
  manual study. Also, be explicit about the setup: sample size,
  population size, number of participants, protocol (each given how
  many sentences, and how disagreement is resolved), etc.}

In the manual study, we sample a set of test cases and corresponding
\lc randomly sampled from seed sentences and expanded sentences from
\tool.  also provided with the sampled test cases. Each subject is
asked for scoring relevancy between the linguistic capability of the
sentences. The score is discrete and it ranges from 1 to 5
representing ``strongly not relevant'' to ``strongly relevant''
respectively. Additionally, the subject scores the relevancy between
sentences and their sentiment labels. The score is also discreate and
ranges from 1 to 5. It represents ``strongly negative'' to ``strongly
positive'' respectively. In this work, we collect manual study scores
from 8 subjects attended. From the collected scores, we measure the
following metrics:

\begin{eqnarray}
  &Reported\:bugs &=\sum_{i} \delta(label_{S^2LCT}!=pred_{model}) \label{metric:rb}\\
  &Incorrect\:inputs &= \sum_{i} \delta(pred_{model}!=label_{human}) \label{metric:ii}
  %% &Label\:inconsistency &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:li}
\end{eqnarray}

The metrics represents the number of data instance that its label
assigned from are different between \tool and its model prediction
(eq~\ref{metric:rb}) and between the model prediction and human
(eq~\ref{metric:ii}). We show the correspondence between \tool and
human by computing the precision and recall from the reported bugs and
incorrect inputs.
%% and between \tool and human (eq~\ref{metric:li}).

\paragraph{RQ2.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate test cases that comprehensively cover the sentences
in a linguistic capability. \tool, instead, automatically generates test cases based on a search
dataset and the syntax in a large reference corpus. We expect \tool can generate a more diverse test suite
than \Cklst. To measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
\sw{Why is this a good metric for diversity?}
Specifically, we use the  \sw{are these metrics we define or are they from ma2018deepgauge?} two coverage metrics in existing work \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), as our metrics to evaluate the test suite diversity.

@@

To answer {\bf RQ2}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds. After that, we randomly select 100 \sw{Why 100, not all?} test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics. 
\cm{we repeat this process and record both the average and variance value of each coverage}
% For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
% Finally, we feed the generated test samples to AdNNs and measure block coverage.
% We repeat this process 10 times and record the average coverage and the variance.
% The results are shown in \tabref{tab:coverage} last two columns.

@@

\paragraph{RQ3.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize

>>>>

\paragraph{\textbf{RQ1 and RQ2}} As described in Section \ref{sec:approach},
\tool generates test cases in two steps: specification-based seed
generation and syntax-based sentence expansion. These automated steps
may generate seed/expanded sentences marked with incorrect sentiment
labels or categorized into wrong linguistic capabilities. For example,
the search rule and template defined in a linguistic capability may
not always generate seed sentences in that capability or with the
correct label.  To answer RQ1 and RQ2, we perform a manual study to
measure the correctness of the sentiment labels and linguistic
capabilities associated with the seed/expanded sentences, produced by
\tool.

In the manual study, we randomly sample three sets of pairs of seed
sentences and corresponding \lc from seed test cases. For each set, we
also select expanded sentences that \tool generated from the formerly
sampled seed sentences. In this experiment, each set has 100 sentences
(50 from seed sentences and 50 from expanded sentences) and 300
sentences, in total, are used for the manual study. For each sampled
set, two subjects are provided with the same set of sampled
sentences. The subjects are asked for scoring the two following:
\textbf{1. relevancy score between sentence and its associated \lc}:
this score measures the amount of appropriateness of the use of
sentence for evaluating the model on its \lc.  The scores are discrete
ranging from 1 to 5, and each represents ``strongly not relevant'' to
``strongly relevant'' respectively. \textbf{2. sentiment score of
  sentence}: this score measures the level of sentence sentiment. It
is also discrete, and it ranges from 1 to 5 representing ``strongly
negative'' to ``strongly positive'' respectively. In this work, we
collect manual study scores from 6 subjects in total. From the
collected scores, we measure the following metrics:

\begin{eqnarray}
  sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
  LC\_relevancy_{AVG} &= \frac{1}{\#data}\cdot\sum_{i} LC\_relevancy_i \label{metric:lcrel}
\end{eqnarray}

The equation~\ref{metric:srel} represent the number of test cases that
their labels assigned from are different between \tool and
human. Higher number of this metric indicates worse correlation of
test oracle that \tool generated with human. In addition, the
equation~\ref{metric:lcrel} represents the average score of the
relevancy score between sentence and its associated \lc. higer average
score means that higher human-level agreement of the use of sentence
for its \lc, resulting in higher suitability of the use of the
testcases for evaluating model on the \lc. Given the metrics, we
answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
and equation~\ref{metric:lcrel} respectively, thereby, show its ability
of \tool to understand human intelligence.

\paragraph{RQ3.}
Recall that a key limitation of \Cklst is that its template-based
approach that relies on significant manual efforts may not generate
test cases that comprehensively cover the sentences in a linguistic
capability. \tool, instead, automatically generates test cases based
on a search dataset and the syntax in a large reference corpus. We
expect \tool can generate a more diverse test suite than \Cklst. To
measure diversity, we follow the approach presented by Ma et
al. \cite{ma2018deepgauge}, where the authors measure the coverage of
NLP model intermediate states as corner-case neurons.  \sw{Why is this
  a good metric for diversity?}  Specifically, we use the \sw{are
  these metrics we define or are they from ma2018deepgauge?} two
coverage metrics in existing work \cite{ma2018deepgauge},
\textit{boundary coverage} (BoundCov) and \textit{strong activation
  coverage} (SActCov), as our metrics to evaluate the test suite
diversity.

@@

To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds. After that, we randomly select 100 \sw{Why 100, not all?} test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics. 
\cm{we repeat this process and record both the average and variance value of each coverage}
% For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
% Finally, we feed the generated test samples to AdNNs and measure block coverage.
% We repeat this process 10 times and record the average coverage and the variance.
% The results are shown in \tabref{tab:coverage} last two columns.

@@

\paragraph{RQ4.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize
